\section{Introduction}

The Common Vulnerability Scoring System (CVSS) is widely used to communicate
the severity of software vulnerabilities. In practice, however, organizations
often rely on the Base score only, even though the real operational severity of
a vulnerability depends on local deployment conditions, business criticality,
security requirements, and mitigating controls.

A previous controlled experiment on CVSS Environmental Metrics showed that
manual assessment does not scale well with environmental complexity. In that
study, assessors were more accurate in a flat network than in a segmented
network, and system-level vulnerabilities were harder to assess correctly than
application-level vulnerabilities in segmented environments~\cite{allodi2017cvssenv}.
The study concluded that automation and data integration are necessary for
environmental assessments to become practical at organizational scale.

This paper continues that line of research. Instead of running another human
subject experiment, we investigate whether a local multi-agent automation
framework can perform the environmental assessment task by collecting and
reasoning over evidence. We use AI Bridge as the execution substrate. AI Bridge
can read local files, run controlled commands, coordinate messages through a
watcher, relay tasks across chats or agents, and produce auditable artifacts.

The main research question is:

\begin{quote}
Can tool-augmented AI agents, operating through AI Bridge, generate reproducible
and evidence-backed CVSS Environmental assessments for segmented PCI-DSS-like
environments?
\end{quote}
