\section{Artifact Validation and Baseline Results}
\label{sec:evaluation}

The current artifact includes a clean deterministic validation run for the PCI segmented lab case. The run is stored in \path{outputs/runs/pci_segmented_lab_20260517_143146/} and is accompanied by \path{run_manifest.json}, input hashes, generated assessments, an audit trace, and a before-after comparison table. These results are treated as artifact-validation results, not as evidence that the watcher workflow outperforms human experts. The evaluation scope is deliberately conservative: it checks reproducibility, traceability, data completeness, label consistency, and dashboard readiness for the deterministic baseline before any broader human-subject or watcher-mediated comparison is claimed. The evaluation scope is deliberately conservative: it checks reproducibility, traceability, data completeness, label consistency, and dashboard readiness for the deterministic baseline before any broader human-subject or watcher-mediated comparison is claimed.


The before-after comparison is summarized in Table~
\
ref{tab:env-effects}. The table is generated from the deterministic run artifacts rather than from manual transcription, so it also acts as a compact reproducibility check for the dashboard and manuscript pipeline.


\
begin{table}[htbp]

\
centering

\
caption{Environmental-score effects in the deterministic PCI segmented lab baseline.}

\
label{tab:env-effects}

\
begin{tabular}{llllrrr}

\
hline
Finding & Asset & CVE & Effect & Before & After & Delta 
\
\
 
\
hline
F-001 & A-CORP-SRV & CVE-2016-0036 & downgraded & 8.8 & 8.0 & -0.8 
\
\
F-002 & POS-01 & CVE-2016-0469 & unchanged & 7.8 & 7.8 & 0.0 
\
\
F-003 & ADMIN-01 & CVE-2016-3234 & downgraded & 8.8 & 8.0 & -0.8 
\
\
F-004 & WIRELESS-LEGACY-01 & CVE-2016-1619 & unchanged & 7.8 & 7.8 & 0.0 
\
\
F-005 & CORE-SW-01 & CVE-2016-6441 & unchanged & 9.7 & 9.7 & 0.0 
\
\
F-006 & CORE-SW-01 & CVE-2016-6428 & unchanged & 8.8 & 8.8 & 0.0 
\
\
 
\
hline

\
end{tabular}

\
end{table}
The run generated 12 assessments for six findings, with one before and one after segmentation assessment per finding. All generated CR, IR, AR, and MAV labels matched the expected expert labels included in the structured case files. Two findings were downgraded after segmentation, four remained unchanged, and none were upgraded. The mean environmental-score delta was -0.267 and the maximum absolute delta was 0.8.

\begin{table}[ht]
\centering
\caption{Clean deterministic before-after run for the PCI segmented lab case.}
\label{tab:clean-run-effects}
\begin{tabular}{lllrrrrl}
\toprule
Finding & Asset & Type & MAV & Before & After & Delta & Effect \\
\midrule
F-001 & A-CORP-SRV & SYS & N--A & 8.8 & 8.0 & -0.8 & downgraded \\
F-002 & POS-01 & SYS & L--L & 7.8 & 7.8 & 0.0 & unchanged \\
F-003 & ADMIN-01 & APP & N--A & 8.8 & 8.0 & -0.8 & downgraded \\
F-004 & WIRELESS-LEGACY-01 & APP & N--N & 7.8 & 7.8 & 0.0 & unchanged \\
F-005 & CORE-SW-01 & SYS & A--A & 9.7 & 9.7 & 0.0 & unchanged \\
F-006 & CORE-SW-01 & SYS & A--A & 8.8 & 8.8 & 0.0 & unchanged \\
\bottomrule
\end{tabular}
\end{table}

The final evaluation will compare four conditions: historical human baseline, deterministic rule-based baseline, language-model baseline without local tool access, and AI Bridge watcher-mediated multi-agent assessment with local evidence access. The primary metrics are exact match for CR, IR, AR, and MAV; secondary metrics include environmental-score error, correct before-after direction, reproducibility across repeated runs, evidence coverage, and audit-trace completeness.





The broader engineering-validation set is summarized in Table~
\
ref{tab:curated-runs}. These additional scenarios are curated case packages used to exercise the deterministic pipeline and artifact summarizer. They extend engineering coverage, but they are not yet treated as independent comparative evidence because external expert review and arm-level adjudication remain future study steps.


\
begin{table}[htbp]

\
centering

\
caption{Curated run summary for deterministic engineering validation.}

\
label{tab:curated-runs}

\
begin{tabular}{lrrrrr}

\
hline
Run & Findings & Assessments & Down & Same & Up 
\
\
 
\
hline
pci_segmented_lab & 6 & 12 & 2 & 4 & 0 
\
\
pci_demo_curated & 10 & 20 & 0 & 10 & 0 
\
\
complex_curated & 10 & 20 & 0 & 10 & 0 
\
\
 
\
hline

\
end{tabular}

\
end{table}

Automated watcher IA validation scope. The current validation workflow is automated and watcher mediated. The pipeline generates evidence linked review rows and reports under validation/ai_review from committed curated artifacts. It does not claim completed independent human expert adjudication. Human expert review is treated as future comparative work rather than a dependency for the present evaluation.


Automated watcher IA validation summary table. 
Automated watcher IA validation outputs were not found during this run.


The automated validation summary table is generated from committed artifacts in article/generated/automated_validation_summary_table.txt and docs/generated/automated_validation_article_inputs.md. It reports watcher IA validation counts and explicitly excludes independent human adjudication claims.


Multi-scenario deterministic pipeline results. The current artifact package includes 
1
 curated scenarios, 
6
 findings, and 
12
 automated environmental CVSS assessments. The deterministic engine classified 
2
 assessments as downgraded, 
4
 as unchanged, and 
0
 as upgraded. These values are generated from committed scenario artifacts and automated watcher IA validation outputs, not from completed independent human expert adjudication.


Trace-enabled evaluation artifacts. The generated comparison CSV files now include per-assessment adjustment traces. This supports inspection of why a finding was downgraded, unchanged, or upgraded under the current prototype scoring policy.


Results package artifacts. The current results package includes curated run summaries, automated watcher IA validation summaries, and adjustment trace summaries. These artifacts provide the basis for the reported scenario totals, decision counts, and traceability claims.

